---
title: "Lab 02 - Plastic waste"
author: "Insert your name here"
date: "Insert date here"
format: html
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

1.  Plot, using histograms, the distribution of plastic waste per capita faceted by continent. What can you say about how the continents compare to each other in terms of their plastic waste per capita?

```{r plastic-waste-continent}
# insert code here
```

### Exercise 2

2.  Recreate the density plots above using a different (lower) alpha level that works better for displaying the density curves for all continents.

2b.
Describe why we defined the `color` and `fill` of the curves by mapping aesthetics of the plot but we defined the `alpha` level as a characteristic of the plotting geom.

```{r plastic-waste-density}
# insert code here
```

### Exercise 3

3.  Describe why we defined the `color` and `fill` of the curves by mapping aesthetics of the plot but we defined the `alpha` level as a characteristic of the plotting geom.

### Exercise 4

4.  Convert your side-by-side box plots from the previous task to [violin plots](http://ggplot2.tidyverse.org/reference/geom_violin.html). What do the violin plots reveal that box plots do not? What features are apparent in the box plots but not in the violin plots?

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

5.  Visualize the relationship between plastic waste per capita and mismanaged plastic waste per capita using a scatterplot. Describe the relationship.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

6.  Colour the points in the scatterplot by continent. Does there seem to be any clear distinctions between continents with respect to how plastic waste per capita and mismanaged plastic waste per capita are associated?

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

7.  Visualize the relationship between plastic waste per capita and total population as well as plastic waste per capita and coastal population. You will need to make two separate plots. Do either of these pairs of variables appear to be more strongly linearly associated?

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

8.  Recreate the following plot, and interpret what you see in context of the data.

```{r recreate-viz}
# insert code here
```
